---
title: "AE 03: Ice cover in Madison, WI area lakes"
---

The data for this application exercise comes from the [lterdatasampler](https://lter.github.io/lterdatasampler/) package. The mission of the [Long Term Ecological Research program (LTER)](https://lternet.edu) Network is to "provide the scientific community, policy makers, and society with the knowledge and predictive understanding necessary to conserve, protect, and manage the nation’s ecosystems, their biodiversity, and the services they provide."

Specifically we'll be using data from the North Temperate Lakes LTER (NTL-LTER) site, which is located in the Madison, WI area, modeling the relationship between number of days that a lake is frozen, excluding periods where the lake thaws before refreezing again, and annual average temperature.

## Getting started

### Packages

We will use the **tidyverse** package for data visualization and wrangling and the **tidymodels** package for modeling.

```{r}
#| label: load-packages
#| message: false
# add code here
```

### Data

The data can be found in the `data` folder; it's called `icecover.csv`.

```{r}
#| label: load-data
#| message: false
# add code here
```

The data dictionary is below:

| Variable Name      | Description                                                      |
|:-------------------|:-----------------------------------------------------------------|
| `lakeid`           | Lake name                                                        |
| `ice_on`           | Date of freeze of lake                                           |
| `ice_off`          | Date of ice breakup of lake                                      |
| `ice_duration`     | Number of days between the freeze and breakup dates of each lake |
| `year`             | Year of observation                                              |
| `annual_avg_temp`  | Annual average air temperature (°C)                              |

## Visualizing the model

We’re going to investigate the relationship between `ice_duration` and `annual_avg_temp`.

- Create an appropriate plot to investigate this relationship. Add appropriate labels to the plot.

```{r}
#| label: visualize
# add code here
```

- If you were to draw a straight line to best represent the relationship between ice duration and annual average temperature, where would it go? Why?

- Now, let R draw the line for you. Refer to the documentation at <https://ggplot2.tidyverse.org/reference/geom_smooth.html>. Specifically, refer to the method section.

```{r}
#| label: visualize-with-line
# add code here
```

- What types of questions can this plot help answer?

- We can use this line to make predictions. Predict what you think the ice duration would be in a year with annual average temperature of 7, 10, and 12 °C. Which prediction is considered extrapolation?

## Model fitting

Fit a model to predict ice duration from average annual temperature.

```{r}
#| label: fit-model
# add code here
```

## Model summary

- Display the model summary including estimates for the slope and intercept along with measurements of uncertainty around them. Show how you can extract these values from the model output.

```{r}
#| label: model-summary
# add code here
```

- Write out your model using mathematical notation.


- What is the interpretation of the estimated coefficients?


## Prediction

Before, you used your lying eyeballs to predict what the ice duration would be in a year with annual average temperature of 7, 10, and 12 °C. Now let's have the computer do it. 

- First, use `R` as an overgrown calculator to compute the model prediction for each of the three temperatures by plugging into your model formula and doing the arithmetic:

```{r}
#| label: predict-by-hand
# add code here
```

- Second, use the `predict` function to perform the same calculation. You should get roughly the same numbers.

```{r}
#| label: predict-by-r
# add code here
```

## Correlation

We can also assess correlation between two quantitative variables.

- What is correlation? What are values correlation can take?

- What is the correlation between temperature and ice duration?

```{r}
#| label: correlation
# add code here
```

## Fitting other models

We can fit more models than just a straight line. Change the plotting code from earlier to use `method = "loess"`. What is different from the plot created before?

```{r}
#| label: visualize-with-curve
# add code here
```
