---
title: "AE 01: The Bechdel Test"
---

In this mini-analysis, we use the data from the FiveThirtyEight story "The Dollar-And-Cents Case Against Hollywood's Exclusion of Women."

This analysis is about the [Bechdel test](https://en.wikipedia.org/wiki/Bechdel_test), a measure of the representation of women in fiction.

## Getting started

### Packages

We'll use the **tidyverse** package for this analysis.

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
```

### Data

The data are stored as a CSV (comma-separated values) file in your repository's `data` folder. Let's read it from there and save it as an object called `bechdel`.

```{r}
#| label: read-data
#| message: false
bechdel <- read_csv("data/bechdel.csv")
```

### Variables of interest

The variables we'll focus on are the following:

-   `title`: name of movie
-   `year`: release year of movie (between 1990 and 2013);
-   `gross_2013`: how much did the movie earn at the box office (in 2013 $);
-   `budget_2013`: how much did the movie cost to make (in 2013 $); 
-   `roi`: Return on investment, calculated as the ratio of the gross to budget;
    - If the movie broke even, roi is ___;
    - If the movie made money, roi is ___;
    - If the movie lost money, roi is ___;
-   `clean_test`: Bechdel test result:
    -   `ok` = passes test
    -   `dubious` (*Chinatown*?)
    -   `men` = women only talk about men
    -   `notalk` = women don't talk to each other
    -   `nowomen` = fewer than two women
-   `binary`: Bechdel Test PASS vs FAIL binary

### Get to know the data

We can use the `glimpse()` function to get an overview (or "glimpse") of the data.

```{r}
#| label: glimpse
# add code here
```

-   What does each observation (row) in the data set represent?

Each observation represents a ___.

-   How many observations (rows) are in the data set?

```{r}
# add code here
```

-   How many variables (columns) are in the data set?

```{r}
# add code here
```

## One numerical variable

Visualize the *distribution* of the film grosses:

```{r}
# add code here
```


Summarize the *distribution* of the film grosses:

```{r}
# add code here
```

What are the features of the distribution (center, spread, and shape)?

## One categorical variable

Visualize the compositon of Bechdel test results:

```{r}
# add code here
```


Summarize the compositon of Bechdel test results:

```{r}
# add code here
```

Which category is most common?

## Two numerical variables

Visualize the relationship between film budgets and grosses:

```{r}
# add code here
```

Summarize the relationship between film budgets and grosses:

```{r}
# add code here
```

How would you describe the relationship in terms of its direction, strength, and shape?

## Numerical and categorical

Visualize the relationship between a film's Bechdel Test result and its return-on-investment:

```{r}
# add code here
```

Summarize the relationship between a film's Bechdel Test result and its return-on-investment:

```{r}
# add code here
```

Does the FiveThirtyEight article's claims hold up?


