---
title: "AE 02: Gerrymandering"
---

## Getting started

### Packages

We'll use the **tidyverse** package for this analysis.

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(usdata)
```

### Data

The data are availale in the **usdata** package.

```{r}
#| label: gerrymander
glimpse(gerrymander)
```

Since this dataset is shipped with a package, it has documentation that you can access via `?gerrymander`. The `flip18` variable is categorical with three levels:

-   -1: control of the district flipped from Democrats to Republicans between 2016 and 2018;
-   0: the district did not flip. If Democrats controlled it in 2016, they kept it in 2018. If Republicans controlled it in 2016, they kept it in 2018;
-   1: control of the district flipped from Republicans to Democrats between 2016 and 2018.


## Flips

Is a Congressional District more likely to have high prevalance of gerrymandering if a Democrat was able to flip the seat in the 2018 election? Support your answer with a visualization as well as summary statistics.

**Hint:** Calculate the conditional distribution of prevalance of gerrymandering based on whether a Democrat was able to flip the seat in the 2018 election.

```{r}
# add code here
```

Add narrative here.


