---
title: "AE 05: Diamonds!"
format: html
---

We want to understand how "The 4 Cs" predict a diamond's price. We have a dataset with 5,000 rows, where each row is a diamond, and along the columns we record each diamond's...

- `price`: in USD;
- `carat`: weight of the diamond;
- `cut`: quality of the cut (Fair, Good, Very Good, Premium, Ideal);
- `color`: diamond colour, from J (worst) to D (best);
- `clarity`: a measurement of how clear the diamond is;
    - I (worst), SI, VS, VVS, IF (best);
- `length_mm`;
- `width_mm`.

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(tidymodels)
```

## Load and prepare the data

```{r}
#| label: load-data
#| message: false
diamonds <- read_csv("data/diamonds.csv")
```

These data have several *categorical* variables: `cut`, `color`, and `clarity`. How are their levels ordered? Does this make sense?

```{r}
#| label: level-ordering

# replace with your code
```

If you don't think that the order of the levels makes sense, use `mutate`, `fct_relevel`, and variable assignment to change it:

```{r}
#| label: re-level

# replace with your code
```

## Exploratory analysis

Visualize the bivariate relationship between `price` and each of the 4 Cs.

```{r}
#| label: price-carat

# replace with your code
```

```{r}
#| label: price-cut

# replace with your code
```

```{r}
#| label: price-clarity

# replace with your code
```

```{r}
#| label: price-color

# replace with your code
```

Put price, carat, and clarity on one plot:

```{r}
#| label: price-carat-clarity

# replace with your code
```

## Empty model

Fit the model for `price` that has no predictors:

```{r}
#| label: empty-model

# replace with your code
```

Interpret the coefficient estimate:

- 

## Simple linear regression

Fit the model that predicts `price` from `carat`:

```{r}
#| label: price-carat-model

# replace with your code
```

Write the equation for the equation of the fitted model:

$$
\widehat{y}=b_0+b_1\times x.
$$

Interpret the coefficient estimates:

- 
- 

## Additive model

Fit the additive model that predicts `price` from `carat` and `clarity`:

```{r}
#| label: price-carat-clarity-model-1

# replace with your code
```

Interpret some coefficient estimates:

- 
- 

## Interaction model

Fit the interaction model that predicts `price` from `carat` and `clarity`:


```{r}
#| label: price-carat-clarity-model-2

# replace with your code
```

Interpret some coefficient estimates:

- 
- 

## "Full" model

Fit the additive model that predicts `price` from all other variables in the dataset:


```{r}
#| label: full-model

# replace with your code
```

## Selection 

Use adjusted $R^2$ to select the "best" model for `price`.

```{r}
#| label: selection

# replace with your code
```


