---
title: "Homework 1"
author: "Insert your name here"
editor: source
format: pdf
---


Load your packages:

```{r}
#| label: load-packages

# add code here
```

Load your data: 

```{r}
#| label: load-data

# add code here
```

## Exercise 0

What music should we listen to while we grade this?


{{< pagebreak >}}

# Part 1

## Exercise 1

Add your response here.

```{r}
#| label: ex-1

# add code here
```

{{< pagebreak >}}

## Exercise 2

Add your response here.

```{r}
#| label: ex-2

# add code here
```

{{< pagebreak >}}

## Exercise 3

Add your response here.

```{r}
#| label: ex-3

# add code here
```

{{< pagebreak >}}

## Exercise 4

Add your response here.

```{r}
#| label: ex-4
#| fig-asp: 1
#| fig-width: 4

# add code here
```

{{< pagebreak >}}

## Exercise 5

Add your response here.

```{r}
#| label: ex-5

# add code here
```

{{< pagebreak >}}

## Exercise 6

Add your response here.

```{r}
#| label: ex-6
#| fig-asp: 1
#| fig-width: 4

# add code here
```

{{< pagebreak >}}

## Exercise 7

Add your response here.

```{r}
#| label: ex-7

# add code here
```

{{< pagebreak >}}

# Part 2: IMS Exercises

## Exercise 8

Add your response here.

## Exercise 9

Add your response here.

## Exercise 10

Add your response here.