---
title: "Homework 4"
author: "Insert your name here"
editor: source
format: pdf
---


Load your packages:

```{r}
#| label: load-packages
#| message: false

# add code here
```

Load your data: 

```{r}
#| label: load-data
#| message: false

# add code here
```

## Exercise 0

What music should we listen to while we grade this?

{{< pagebreak >}}

# Part 1: lifting and model selection

## Exercise 1

### part a

```{r}
#| label: lifting-data-prep

# add code here
```

### part b

```{r}
#| label: lifting-best-model

# add code here
```

### part c

Add your response here.

### part d

Add your response here.

### part e

Add your response here.

{{< pagebreak >}}

# Part 2: GSS and logistic regression

## Exercise 2

```{r}
#| label: gss-data-prep

# add code here
```

## Exercise 3

### part a

```{r}
#| label: advfront-educ-fit

# add code here
```

### part b

$$
\log\left(\frac{\hat{p}}{1-\hat{p}}\right) = ???
$$

### part c

Add your response here.

### part d

```{r}
#| label: predict

# add code here
```


## Exercise 4

### part a

```{r}
#| label: advfront-educ-polviews-fit

# add code here
```

### part b

$$
\log\left(\frac{\hat{p}}{1-\hat{p}}\right) = ???
$$

### part c

Add your response here.

```{r}
#| label: selection

# add code here
```

{{< pagebreak >}}

# Part 3: IMS exercises

## Exercise 5

Add your response here.

## Exercise 6

Add your response here.




