---
title: Lab 4
subtitle: Duke University - STA 101 - Fall 2026
authors: 
  - Your Name
  - Teammate 1
  - Teammate 2
  - Teammate 3
format: pdf
fig-width: 5
fig-asp: 0.618
---

```{r}
#| label: load-packages-data
#| message: false
# add code here
```


# Task 0

```{r}
#| label: task-0
# add code here
```

{{< pagebreak >}}

# Task 1

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-1
# add code here
```

{{< pagebreak >}}

# Task 2

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-2
# add code here
```

$$
\widehat{y} = b_0 + b_1 \times x.
$$

Interpret: 

- 
-


{{< pagebreak >}}

# Task 3

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-3
# add code here
```

Interpret: 

- 
-
-
-

{{< pagebreak >}}

# Task 4

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-4
# add code here
```

Type an equation:

$$
\widehat{y} = b_0 + b_1 \times x.
$$

Type another equation:

$$
\widehat{y} = b_0 + b_1 \times x.
$$

Type yet another equation:

$$
\widehat{y} = b_0 + b_1 \times x.
$$

{{< pagebreak >}}

# Task 5

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-5
# add code here
```

{{< pagebreak >}}


# Task 6

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-6
# add code here
```




