---
title: Lab 2
subtitle: Duke University - STA 101 - Fall 2026
authors: 
  - Your Name
  - Teammate 1
  - Teammate 2
  - Teammate 3
format: pdf
fig-width: 5
fig-asp: 0.618
---

```{r}
#| label: load-packages-data
#| message: false
# add code here
```

# Task 1

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-1
# add code here
```

{{< pagebreak >}}

# Task 2

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-2
# add code here
```

{{< pagebreak >}}

# Task 3

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-3
# add code here
```

{{< pagebreak >}}

# Task 4

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-4
# add code here
```

{{< pagebreak >}}

# Task 5

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-5
# add code here
```

{{< pagebreak >}}


# Task 6

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-6
# add code here
```

{{< pagebreak >}}


# Task 7

Add any narrative here (or delete if you don't need it).

```{r}
#| label: task-7
# add code here
```

{{< pagebreak >}}


# Task 8

Add narrative here.







